Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-07-25 Report/decomposition_solutions.tex
to read

The distributed precoder designs for the proposed \ac{JSFRA} scheme are discussed in this section. The convex formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}. In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are based on the \acl{PD} and the \ac{ADMM} are considered herein.

Let us consider the convex subproblem with the fixed receive beamformers \me{\mvec{w}{l,k,n}} presented in \eqref{eqn-9} based on the Taylor series approximation for the nonconvex constraint. The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well. Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
\begin{IEEEeqnarray}{rCl} \label{eqn-decent-1} \allowdisplaybreaks  \neqsub
&\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}}& \quad \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
&\text{subject to}& \quad \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviations corresponding to users \me{k \in \mc{U}_b}.

>>>>

In this section, we discuss the distributed precoder designs for the solutions in Sections \ref{sec-3.2.1} and \ref{sec-3.3} for \eqref{eqn-6}. Note that the convex formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the \acp{BS} in \eqn{\mc{B}}. In order to design the precoders independently at each \ac{BS} with a minimal information exchange via backhaul, iterative decentralization methods based on the \acl{PD} and the \ac{ADMM} are considered herein.

Let us consider the convex subproblem with fixed receive beamformers \me{\mvec{w}{l,k,n}} presented in \eqref{eqn-9} based on the \ac{SINR} relaxation for the nonconvex constraint in \eqref{eqn-6.2}. The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well. Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
\begin{IEEEeqnarray}{rCl} \label{eqn-decent-1} \allowdisplaybreaks  \neqsub
&\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}}& \quad \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
&\text{subject to}& \quad \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviations corresponding to users \me{k \in \mc{U}_b}.

### 2015-07-25 Report/dual_approach.tex
to read

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual vector for the next iteration is updated by using the subgradient search to maximize the dual objective as
\begin{equation}
\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right )
\label{dual-sg-update}
\end{equation}
where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model under consideration. The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}. For our simulation models, we consider step size parameter \me{\rho=2}. The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates. The distributed precoder design using the \ac{ADMM} approach is shown in Algorithm \ref{algo-3}. The convergence analysis of the distributed algorithms are discussed in Appendix \ref{sec-dist-conv}.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
				\me{j = j + 1}\;
			}
			precoded downlink pilot transmission with \me{\mvec{m}{l,k,n}}\;
			update \me{\mvec{w}{l,k,n}} to all \acp{BS} in \me{\mc{B}} using precoded uplink pilots \cite{komulainen2013effective}\;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$, \me{j=0} \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}

\begin{comment}
The \ac{ADMM} decomposition method is based on the \acl{DD}, however it shows better convergence properties. In contrast to the \acl{PD} problem, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}. In order to decouple the problem \eqref{eqn-decent-1}, the coupling variables \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3} are replaced by the respective local copies \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}, which are then solved for an optimal solution. Now the sub problems are coupled by the global consensus vector \me{\mbfa{\zeta}} maintaining the complete stacked  interference profile of all users in the system as
\begin{IEEEeqnarray}{ll}
	\mbfa{\zeta} &= \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1}, \right. \nonumber \\
	& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \eqspace \IEEEyessubnumber \\
	n_{b_k} &= |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |. \IEEEyessubnumber
\end{IEEEeqnarray}

>>>>

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual vector for the next iteration is updated by using the subgradient search to maximize the dual objective as
\begin{equation}
\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right )
\label{dual-sg-update}
\end{equation}
where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model under consideration. The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}. In numerical simulations, we consider step size \me{\rho=2}. The above iterative procedure is performed until convergence or terminated when exceeding a predetermined number of iterations, say, \eqn{J_{\max}}. The \ac{ADMM} based precoder design is outlined in Algorithm \ref{algo-3}.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
				update \me{j = j + 1}\;
			}
			send precoded downlink pilot with \me{\mbf{m}}\;
			evaluate \me{\mvec{w}{l,k,n}} at each user and inform to all \acp{BS} in \eqn{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective} \;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$, \me{j=0} \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}

The convergence analysis for the distributed algorithms is provided in Appendix \ref{sec-dist-conv}. \review{In practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of steps, say, \eqn{J_{\max}}. If so, the convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. It follows from the fact that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence. However, if the distributed algorithms are performed for adequate number of iterations to ensure strict monotonicity of the objective in each \ac{SCA} step, then the limit point of the sequence of iterates is a stationary point of \eqref{eqn-6}.}

\begin{comment}
\begin{algorithm}
\SetAlgoLined
\DontPrintSemicolon
\BlankLine
\SetKwInput{KwInit}{Initialize}
\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
\ForEach{\ac{BS} \me{b \in \mc{B}}}{
\Repeat{convergence or \me{i \geq I_{\max}}}{
\Repeat{convergence or \me{j \geq J_{\max}}}{
solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
\me{j = j + 1}\;
}
precoded downlink pilot transmission with \me{\mvec{m}{l,k,n}}\;
update \me{\mvec{w}{l,k,n}} to all \acp{BS} in \me{\mc{B}} using precoded uplink pilots \cite{komulainen2013effective}\;
update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
$i = i + 1$, \me{j=0} \;
}
}
\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
\label{algo-3}
\end{algorithm}
The \ac{ADMM} decomposition method is based on the \acl{DD}, however it shows better convergence properties. In contrast to the \acl{PD} problem, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}. In order to decouple the problem \eqref{eqn-decent-1}, the coupling variables \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3} are replaced by the respective local copies \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}, which are then solved for an optimal solution. Now the sub problems are coupled by the global consensus vector \me{\mbfa{\zeta}} maintaining the complete stacked  interference profile of all users in the system as
\begin{IEEEeqnarray}{ll}
	\mbfa{\zeta} &= \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1}, \right. \nonumber \\
	& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \eqspace \IEEEyessubnumber \\
	n_{b_k} &= |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |. \IEEEyessubnumber
\end{IEEEeqnarray}

### 2015-07-25 Report/introduction.tex
to read

%The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks. The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which impacts the mobile battery consumption. In order to overcome the receiver complexity, \ac{OFDM} is introduced for the wide band transmissions. To improve data rate, multiple antennas are installed at \acp{BS} and/or at user terminals to avail additional freedom in the form of spatial dimension. The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the different users present in the network. We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets in the \acp{BS}. Since the resources are shared by multiple users associated with different \acp{BS}, the problem of interest can be viewed as a resource allocation one.

In general, the resource allocation problems such as admission control ones can be formulated by assigning a binary variable for each user to indicate the presence or absence of a particular resource \cite{admission_control}. Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables. After the design stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource. A zero transmit precoder indicates the absence of the user on a given resource. In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergences.
%The queue minimizing network optimization objective is used to design the beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets. To achieve the best performance, we propose a joint resource allocation scheme over the space and frequency dimensions among the coordinating \acp{BS} to minimize the time that the packets stay in the queues prior to the transmission, and, hence, to avoid packet drops as an indirect objective.

The queue minimizing precoder designs are closely related to the \ac{WSRM} problem with additional rate constraints to limit the throughput beyond the number of backlogged packets associated with the users. The topics on \ac{MIMO} \ac{IBC} precoder design have been studied extensively with different performance criteria in the literature. Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, \ac{SCA} approach has become a powerful tool to deal with these problems. For example, in \cite{sin_algorithm}, the nonconvex part of the objective is linearized around an operating point to solve the \ac{WSRM} problem in a iterative manner. A similar approach using arithmetic-geometric inequality was proposed in \cite{tran2012fast}.

The relation between the achievable sum rate and the \ac{MSE} of the received symbol by using fixed \ac{MMSE} receivers can be used to solve the \ac{WSRM} problem \cite{mse_duality}. In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients. In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders. Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the other variables are fixed. The \ac{MSE} reformulation for the \ac{WSRM} problem was also studied in \cite{hong2012decomposition} by using \ac{SCA} to solve the problem in an iterative manner. Moreover, distributed precoder designs with \ac{QoS} requirements as additional rate constraints are studied for the \ac{MSE} reformulated \ac{WSRM} problem in \cite{kaleva2013primal,kaleva2013decentralized}.

>>>>

%The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks. The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which impacts the mobile battery consumption. In order to overcome the receiver complexity, \ac{OFDM} is introduced for the wide band transmissions. To improve data rate, multiple antennas are installed at \acp{BS} and/or at user terminals to avail additional freedom in the form of spatial dimension. The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the different users existing in the network. We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets in the \acp{BS}. Since the resources are shared by multiple users associated with different \acp{BS}, the problem of interest can be viewed as a resource allocation one.

In general, the resource allocation problems such as admission control ones can be formulated by assigning a binary variable for each user to indicate the presence or absence of a particular resource \cite{admission_control}. Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables. After the design stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource, and the zero transmit precoder indicates the absence of the user on a given resource. In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergence.
%The queue minimizing network optimization objective is used to design the beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets. To achieve the best performance, we propose a joint resource allocation scheme over the space and frequency dimensions among the coordinating \acp{BS} to minimize the time that the packets stay in the queues prior to the transmission, and, hence, to avoid packet drops as an indirect objective.

The queue minimizing precoder designs are closely related to the \ac{WSRM} problem with additional rate constraints to limit the throughput beyond the number of backlogged packets associated with the users. The topics on \ac{MIMO} \ac{IBC} precoder design have been studied extensively with different performance criteria in the literature. Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, \ac{SCA} approach has become a powerful tool to solve these problems. For example, in \cite{sin_algorithm}, the nonconvex part of the objective is linearized around a fixed operating point to solve the \ac{WSRM} problem in a iterative manner. A similar approach using arithmetic-geometric inequality was proposed in \cite{tran2012fast}.

The relation between the achievable sum rate and the \ac{MSE} of the received symbol by using fixed \ac{MMSE} receivers can also be used to solve the \ac{WSRM} problem \cite{mse_duality}. In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients. In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and receivers. Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the other variables are fixed. The \ac{MSE} reformulation for the \ac{WSRM} problem was also studied in \cite{hong2012decomposition} by using \ac{SCA} to solve the problem in an iterative manner. Moreover, distributed precoder designs with \ac{QoS} requirements as additional rate constraints are studied for the \ac{MSE} reformulated \ac{WSRM} problem in \cite{kaleva2013decentralized}.

### 2015-07-25 Report/kkt_mse_approach.tex
updated noise information in KKT solutions
to read

In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}. In contrast to Sections \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same time to minimize the global queue deviation objective with few number of iterations. \review{The alterantive way is motivated by the fact that the distributed approaches presented in the preceeding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.}

In this section, we provide an algorithm that can be of practical importance owing to lower signaling requirements. We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter. Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}. Since the work in \cite{kaleva2013decentralized,kaleva2013primal} are similar to that of the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, the formulations require explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.

@@

\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}\\

@@

	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6} \\

>>>>

In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}. In contrast to Sections \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same time to minimize the global queue deviation objective with few number of iterations. \review{The alternative way is motivated by the fact that the distributed approaches presented in the preceeding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.}

In this section, we provide an algorithm that can be of practical importance owing to lower signaling requirements. We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter. Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized}. Since the work in \cite{kaleva2013decentralized} are similar to that of the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, the formulations require explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.

@@

\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + N_0 \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}\\

@@

	& \qquad {} + N_0 \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6} \\
